---
title: "RWorksheet#5_group(1&9)"
author: "GROUP 1&9 BSIT-2B"
date: "2023-11-30"
output:
  pdf_document: default
  html_document: default
---
 

##Extracting TV Shows Reviews

1. Each group needs to extract the top 50 tv shows in Imdb.com. It will include the rank, the title of the
tv show, tv rating, the number of people who voted, the number of episodes, the year it was released.

```{r}
library(rvest)
library(httr)
library(dplyr) 
library(polite)
library(stringr)

  
polite::use_manners(save_as = 'polite_scrape.R')

url <- 'https://m.imdb.com/chart/toptv/?ref_=nv_tvv_250'

session <- bow(url, user_agent = "Educational")
session

title_show <- character(0)
list_year_ep <-character(0)
 
title_show <- scrape(session) %>%
  html_nodes('h3.ipc-title__text') %>% 
  html_text
 
title_show_only <- as.data.frame(title_show[2:51])
title_show_only
colnames(title_show_only) <- "Rank"

show_df <- strsplit(as.character(title_show_only$Rank),".",fixed = TRUE)
show_df <- data.frame(do.call(rbind,show_df))

show_df <- show_df[-c(3:5)] 

#renaming column 1 and 2
colnames(show_df) <- c("Rank","Title") 
 
 
list_year_ep <- scrape(session) %>%
  html_nodes('span.sc-479faa3c-8.bNrEFi.cli-title-metadata-item
') %>% 
  html_text
years_only <- c()

for (i in seq(1, length(list_year_ep), by = 3)) {
  years_only <- c(years_only, list_year_ep[i])
} 
Year <- years_only[1:50]

ep_only <- c()
for (i in seq(2, length(list_year_ep), by = 3)) {
  ep_only <- c(ep_only, list_year_ep[i])
}
Episode <- ep_only[1:50]

df_title_ep <- data.frame(Episode, Year)

df_title_ep$Year <- gsub("^(\\d{4}).*", "\\1", df_title_ep$Year)

colnames(df_title_ep) <- c("Number Of Episodes", "Year Released") 

list_rating <- scrape(session) %>%
  html_nodes('span.ipc-rating-star.ipc-rating-star--base.ipc-rating-star--imdb.ratingGroup--imdb-rating') %>% 
  html_text()

wholeRATING <- as.data.frame(list_rating[1:50])
colnames(wholeRATING) <- "Rating"

wholeRATING$Rating <- gsub("\\s*\\([^)]+\\)\\s*", "", wholeRATING$Rating)
wholeRATING$Vote_Count <- gsub(".*\\(([^)]+)\\)", "\\1", list_rating[1:50])


df_rating_vote <- wholeRATING
colnames(df_rating_vote) <- c("Rating","Vote Count") 


final_df <- cbind(show_df, df_rating_vote,df_title_ep )
final_df
```
 
From the 50 tv shows, select at least 5 tv shows to scrape the user reviews that will include the
reviewer’s name, date of reviewed, user rating, title of the review, and text reviews.
 
```{r}
 
tv_show_urls <- c(
  "https://www.imdb.com/title/tt0081846/reviews",  # COSMOS
  "https://www.imdb.com/title/tt0903747/reviews",  # BREAKING BAD
  "https://www.imdb.com/title/tt0185906/reviews",  # BAND OF BROTHERS
  "https://www.imdb.com/title/tt7366338/reviews",  # CHERNOBYL
  "https://www.imdb.com/title/tt0417299/reviews"   # Avatar: The Last Airbender
)

all_shows<-list()
 
for (url in tv_show_urls) {
  page <- read_html(url)

  reviewers_name <- page %>% html_nodes(".display-name-link") %>% html_text()
  dates <- page %>% html_nodes("span.review-date") %>% html_text()
  user_ratings <- page %>% html_nodes("span.rating-other-user-rating") %>% html_text()
  text_reviews <- page %>% html_nodes("div.text") %>% html_text()

  tvshow_reviews_df <- data.frame(
    Reviewer_Name = reviewers_name[1:25],
    Date = dates[1:25],
    User_Rating = user_ratings[1:25],
    Text_Review = text_reviews[1:25]
  )
all_shows[[url]] <- tvshow_reviews_df

}
final_reviews_df <- do.call(rbind, all_shows)
colnames(final_reviews_df) <- c("Name", "Date of Review", "User Rating", "Text Reviews")
rownames(final_reviews_df) <- NULL


final_reviews_df
```
3. Create a time series graph for the tv shows released by year. Which year has the most number of tv
shows released?

```{r}

 library(ggplot2)

ggplot(final_df, aes(x = Year, y = Episode, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "red") +
  labs(title = "TV Shows Released by Year",
       x = "Year Released",
       y = "Number of TV Shows") +
  theme_minimal()
```



4. Select 3 products from Amazon of the same category. Extract the price, description, ratings and
reviews of each product.

```{r}
url<-"https://www.amazon.com/s?k=tee+back+tank+tops&crid=1OB1A9SM5CVRK&sprefix=%2Caps%2C456&ref=nb_sb_ss_recent_1_0_recent"

session<-bow(url, user_agent = "Educational")
session

prices<- character(0)
ratings<- character(0)

prices<-scrape(session)%>%
  html_nodes('span.a-price-whole')%>%
  html_text

ratings<-scrape(session)%>%
  html_nodes('span.a-icon-alt')%>%
  html_text

prices_ratings<-data.frame(prices[2:4],
                           ratings[2:4]
                          
                           )
 

colnames(prices_ratings) <- c("Price", "Overall Rating");
 
teeback_urls<-c(
  "https://www.amazon.com/TELALEO-Athletic-Racerback-Activewear-Sleeveless/dp/B08T1Z7FP1/ref=sr_1_5?crid=1OB1A9SM5CVRK&keywords=tee+back+tank+tops&qid=1701518421&sprefix=%2Caps%2C456&sr=8-5",#6, 5,or 3 pack
  "https://www.amazon.com/Aeuui-Workout-Racerback-Shirts-Clothes/dp/B088CYZNKS/ref=sr_1_6?crid=1OB1A9SM5CVRK&keywords=tee+back+tank+tops&qid=1701518421&sprefix=%2Caps%2C456&sr=8-6",#Verdusa Women
  "https://www.amazon.com/SOLY-HUX-Womens-Sleeveless-Shirts/dp/B0BYD8H1DZ/ref=sr_1_8?crid=1OB1A9SM5CVRK&keywords=tee+back+tank+tops&qid=1701518421&sprefix=%2Caps%2C456&sr=8-8"#SOLY HUX
)

all_reviews<-list()
 
for(url in teeback_urls){
  page<-read_html(url)
  
user_comment<-page%>%html_nodes('span.a-size-base.review-text')%>%
    html_text()


user_descr<-page%>%html_nodes('span.a-list-item.a-size-base.a-color-base')%>%
  html_text()

    user_comment_cleaned <- str_trim(user_comment[2:4])

  reviews.df<-data.frame(user_comment_cleaned,
                         user_descr[2:4])
all_reviews[[url]]<-reviews.df


 
}  
colnames(reviews.df)<-c("Product Review", "Product Description")

do.call(rbind, reviews.df)
View(reviews.df)


final_amazon_scrape<-cbind(prices_ratings,reviews.df)
final_amazon_scrape

```